%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Nagy} \headerlastnamestyle{Salem} \\
	\vspace{1mm}
	{\faEnvelope\ me@muhnagy.com} | {\faMapMarker\ Tallinn, Estonia} | {\faLink\ muhnagy.com} | \href{http://www.github.com/muhammednagy}{\faGithub\ muhammednagy}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{B.Sc in Software development and entrepreneurship}
	{Estonian Entrepreneurship University Of Applied Sciences}
	{Tallinn, Estonia}
	{Feb 2019 – Present}
	{}
\end{cventries}

\vspace{-8mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Employment}
\begin{cventries}
	\cventry
	{Software Developer}
	{Shopz.com}
	{Tallinn, Estonia}
	{May 2020 – Present}
	{\begin{cvitems}
		\item {Working on building the backend for web shops solutioins in Go.}
		\item {Building dynamioc template switching in runtime and dynamic template elements rendering.}
		\end{cvitems}}
	\cventry
	{Software Developer}
	{Mindly}
	{Tallinn, Estonia}
	{December 2019 – May 2020}
	{\begin{cvitems}
		\item {Worked on building a modern front end using Vue.js and added features for the backend in Ruby on Rails for a famous debt collecting company in the Baltics and Finland.}
		\item {Worked on optimizing a search engine API for data fetched from different legal institutions all over the world for a famous identity verification company that used Ruby on Rails and PostgreSQL. Managed to make the search work faster by over 90 \%.}
		\end{cvitems}}
	\cventry
	{Growth Specialist}
	{Paxful}
	{Tallinn, Estonia}
	{Aprill 2019 – November 2019}
	{\begin{cvitems}
		\item {Worked on increasing the user base in the MENA region and restructuring the company and the way it works internally.}
		\end{cvitems}}
	\cventry
	{Software Developer}
	{Bixer}
	{Singapore (Remote)}
	{August 2018 – April 2019}
	{\begin{cvitems}
		\item {Worked on the backend of the application as well as managing the infrastructure.}
		\item {Was maintaing and managing 2 crypto exchanges operating the Southeast Asia region.}
		\end{cvitems}}
	\cventry
	{CTO/Co-founder}
	{Infraex Development}
	{TN, USA (Remote)}
	{October 2017 – July 2018}
	{\begin{cvitems}
		\item {Re-engineered market exchange software to suit each customer’s needs.}
		\item {Worked with partners in various global jurisdictions to ensure that they met local regulations and implemented legally required identity verification.}
		\item {Helped clients launch crypto exchanges in almost all continents and provided support.}
		\end{cvitems}}
	\cventry
	{Linux System Administrator, Internship}
	{Spirula Systems}
	{Alexandria, Egypt}
	{June 2017 – August 2017}
	{\begin{cvitems}
		\item {Learned Ansible, Bash and other DevOps tools built over the period of the internship.}
		\end{cvitems}}
	\cventry
	{Software Developer, Internship}
	{eSpace}
	{Alexandria, Egypt}
	{June 2016 – August 2016}
	{\begin{cvitems}
		\item {Worked on building a MOOC web platform that is similar to Coursera that was used to host company tech talks and internal courses Using Ruby on Rails.}
		\end{cvitems}}
\end{cventries}

\vspace{-7mm}

\cvsection{Open-source Projects}
\begin{cventries}
	\cventry
	{Open source crypto exchange platform.}
	{Peatio}
	{Ruby, Rails, Bitcoin, Ethereum}
	{http://github.com/muhammednagy/peatio}
	{}
	
	\vspace{-6mm}
	\cventry
	{Gearbox is a web framework written in Go with a focus on high performance and memory optimization.}
	{Gearbox}
	{Go}
	{https://github.com/gogearbox/gearbox}
	{}
	
	\vspace{-6mm}
\end{cventries}

\cvsection{Awards}
\begin{cvhonors}
	\cvhonor
	{Bounty}
	{KiwEth, Quorum blockhain deployment tool.}
	{JPMorgan ETHParis}
	{March 2019}
	\cvhonor
	{Bounty}
	{An Ether payment button for websites and apps with an incentive system behind it.}
	{Skale ETHNewYork}
	{May 2019}
	\cvhonor
	{Bounty}
	{Squirrel Goals is an Ethereum dApp that helps you save money.}
	{Skale ETHBerlin}
	{August 2019}
\end{cvhonors}
\ 
\end{document}